Pillar 1 - Sequential Pattern Mining

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplified d_cumulative_transcript

### Transcript with Preceding courses per student
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    course_all  = paste(unique(d_transactions$item), collapse = " "),
    course_all  = str_split(course_all, pattern = " "),

    course_now  = str_split(item, pattern = " "),

    course_past     = Reduce(paste, item, accumulate=T),
    course_past     = lag(course_past),
    course_past     = str_split(course_past, pattern = " ")) %>%
  ungroup() %>%
    mutate(
    course_past_now = purrr::map2(.x = course_past,
                                      .y = course_now,
                                      .f = union),
    course_not = purrr::map2( .x = course_all,
                              .y = course_past_now,
                              .f = setdiff)
    ) %>%
  mutate(item = str_split(item, pattern = " "))
```

>>>>

### Transcript with Preceding courses per student
```{r}

#
# List of all courses
course_all <- unique(d_transactions$taken_PF_HL$item)

#
# courses taken so far and not taken so far
d_cumulative_transcript <- d_transactions$taken_PF_HL %>%

  group_by(
    sequenceID,
    eventID
    ) %>%
  summarize(
    course_current = list(
      unique(item)
      )
    ) %>%

  group_by(
    sequenceID
    ) %>%
  mutate(
    course_past = Reduce(
      f = paste, 
      x = course_current, 
      accumulate = TRUE
      ) %>%
      lag
    ) %>%

  rowwise %>% # equivalent to "group by row"
  mutate(
    course_so_far     = list(union  (course_past, course_current)),
    course_not_so_far = list(setdiff(course_all , course_so_far ))
    ) %>%
  ungroup

rm(course_all)
```
